Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-12 treestats_paper.tex
one more citation

\paragraph{Future work}
In this paper,
we have considered only so-called additive, single site statistics.
Extensions to statistics involving the pairwise joint distribution of genotypes across sites,
such as linkage disequlibrium are planned for future work.
Haplotype-based statistics may require different classes of algorithms.

>>>>

\paragraph{Future work}
In this paper,
we have considered only so-called additive, single site statistics.
Extensions to statistics involving the pairwise joint distribution of genotypes across sites
\citep[as used by][]{hudson2001twolocus},
such as linkage disequlibrium are planned for future work.
Haplotype-based statistics may require different classes of algorithms.
